---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=8, fig.height=12
)
```

# gtex_tissue_palette

<!-- badges: start -->

<!-- badges: end -->

The goal of gtex_tissue_palette is to provide a tab-delimited table of GTEx tissue labels, associated colour HEX and RGB codes.

Data wrangled from the Broad Institute files
[gene expression by tissue](https://github.com/broadinstitute/gtex-public/blob/master/scripts/gene_expression_by_tissue.py) and
[colors.json](https://raw.githubusercontent.com/broadinstitute/gtex-viz/7cfffd65f19fbcad216a0df3325cfd89e40d6952/boxplot/dev/colors.json)


```{r,message=F,warning=F}
library(tidyverse)
```

## Read data

```{r }

setwd('~/Git/gtex_tissue_palette/')
gtx_tissue_col <- read_rds('gtex_tissue_col_hex.Rds')

```

```{r}

gtx_tissue_col %>% arrange(desc(tissue_paste)) %>% tidyExt::print_all()
```

Note [**gtex_tissue_col_hex.tsv**](https://github.com/bansell/gtex_tissue_palette/blob/main/gtex_tissue_col_hex.tsv) is also provided, but this does not preserve the factor order for plotting.

```{r,include=F,eval=F}
DT::datatable( gtx_tissue_col,
              rownames = FALSE,
              caption = "GTEx Tissue Colours",
              filter = "top",
              extensions = c('Buttons',  'Scroller'),
              options = list(
                  dom = 'Bfrtip',
                  buttons = c('copy', 'csv', 'excel'),
                  deferRender = TRUE,
                  scrollY = 400,
                  scroller = TRUE
                )
              ) 

```

To enforce the alphabetical order on the vertical axis if using gtex_tissue_col_hex.tsv:

```{r,eval=F}
gtx_tissue_col <- gtx_tissue_col %>% 
  arrange(desc(tissue_paste)) %>%
   mutate(across(.fns=~fct_inorder(.)))
  
```

## Plot the palette

```{r,message=F,warning=F,dpi=300,out.height="175%",out.width="100%"}

gtx_tissue_col %>% 
  ggplot(aes(y=tissue_hr,x="",fill=tissue_color_hex)) + 
  geom_tile(col='white',lwd=0.75,show.legend = F,cex=5) +
  geom_text(aes(label=tissue_color_hex),cex=3) +
  scale_fill_identity()+ theme_classic() + xlab('') + ylab('')

```


<!-- devtools::build_readme()  -->

